
\chapter*{Acknowledgements}
\label{chap:acknowledgements}

First of all, I would like to express my sincere appreciation to my supervisors,
Dr. Ir. G. \textsc{Vandewiele}, Ing. B. \textsc{Steenwinckel}, and Dr. Ir.
S. \textsc{Cremer}. My heartfelt thanks to Dr. Ir. G. \textsc{Vandewiele}, who,
with his experience and knowledge, guided me throughout this Master's
thesis. Dr. Ir. G. \textsc{Vandewiele} was the supervisor that any student
would want to have. He was always there to help and give good advice. I would
also like to thank Ir. B. \textsc{Steenwickel}, who also played an essential
role in this work. Ir. B. \textsc{Steenwickel} also helped me get the job
done. Finally, I would like to thank Dr. Ir. S. \textsc{Cremer} for his advice
in the elaboration of this Master's thesis and for having accepted to supervise
me.

\medskip

\noindent I would also like to express my gratitude to
Prof. Dr. F. \textsc{Ongenae}, who gave her approval to realize this Master's
thesis and directly accepted me with welcome arms.

\medskip

\noindent I wish to extend my special thanks to Dr. P. \textsc{Colpaert} for
allowing me to get in touch with imec and the IDLab research center. Without his
help, this experience would not have been possible.

\medskip

\noindent I want to express my gratitude to the Haute École in Hainaut to
achieve this Master's thesis and to thank every teacher for having passed on
their knowledge to me. Special attention to Ing. L. \textsc{Isidoro},
MSc. Ir. J-S. \textsc{Lerat}, BSc. Y. \textsc{Pietrzak},
MSc. L. \textsc{Remacle}, and Ing. G. \textsc{Tricarico} for their kindness,
their passion, and for having made me want to continue these studies.

\medskip

\noindent I would also like to thank my friends, whom I have met during these
years of study and who, through their words, their motivation, and the many
memories I have shared with them, have made my life better. In particular, I
would like to thank C. \textsc{Bruyère}, I. \textsc{Delsarte},
V. \textsc{Denis}, S. \textsc{Eker}, N. \textsc{Luongo}, G. \textsc{Quittet},
and T. \textsc{Simon}. A particular thought to my childhood friend,
H. \textsc{Koch}, who followed my evolution since the beginning of my teen years
and has always been of great help.

\medskip

\noindent Finally, I would like to dedicate this Master's thesis to my family
and, more particularly, to my great-grandfather and my grandmother. Throughout
these years of study, they have always supported me. My life would have taken a
different path without you. I hope that I can one day be as good a person as you
are.

\thispagestyle{empty}
\clearpage

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../report"
%%% End: